%%%%%%%%%%%%%%%%%
% This is a two-column CV template based on moderncv.cls
% (v1.0, May 16 2024) written by Genki Ogaki (rockstarogk@gmail.com). Compiles with XeLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

% environment
\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{banking}
\nopagenumbers{}

\usepackage[T1]{fontenc}
\usepackage{inputenc}
\usepackage[a4paper, top=1cm, bottom=0.5cm, left=0.8cm, right=0.8cm]{geometry}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{paracol}
\usepackage{qrcode}
\usepackage{enumitem}  
\usepackage{multicol}
\usepackage{titlesec}

\usepackage{fontspec}
\setmainfont{Lato}

\definecolor{brandblue}{HTML}{0A66C2} % choose any hex you like

\definecolor{darkblue}{HTML}{0B1D51} % deep dark blue


% Основной текст = 10pt (чуть плотнее межстрочный)
\renewcommand\normalsize{\fontsize{10}{12}\selectfont}

\renewcommand\small{\fontsize{9}{10}\selectfont}

% Подзаголовки = 11pt
\titleformat{\subsection}{\fontsize{11}{13}\bfseries}{}{0pt}{}

% Заголовки секций = 12pt
\titleformat{\section}
  {\vspace{2mm}\fontsize{14}{14}\color{brandblue}\bfseries\scshape} % стиль текста
  {}{0pt}{}                            % без номера, без отступа
  [\titlerule\vspace{1mm}]
  
\titlespacing*{\section}{0pt}{0.8ex}{0.6ex}
\titlespacing*{\subsection}{0pt}{0.6ex}{0.4ex}


% macro
\renewcommand*{\labelitemi}{-}

\makeatletter
\renewcommand\footnotesize{\@setfontsize\footnotesize{10}{12}}
\makeatother

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand{\educationentry}[8][]{
  \noindent
  \textbf{#4} (#7) \hfill \textbf{#2} \\[0.1em] % University name and location
  \textit{#3} \hfill \textit{#6} \\[0.3em] % Degree and program, study period
  \textbf{Major:} #5 \\[0.5em]
  \textbf{Coursework:}
  \vspace{0.5em}
  {\footnotesize
    \raggedcolumns
      \small
      \begin{itemize}[leftmargin=1.2em, itemsep=0.1em, topsep=0em, parsep=0em]
        #8
      \end{itemize}
  } 
}

% preamble
\familyname{Simon Mokrov}
\address{Amsterdam, the Netherlands}{}
\title{Frontend Developer}

% document
\begin{document}
\maketitle
\vspace{-7mm}

\section{CONTACTS}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l l l @{}}
  \emailsymbol\enspace \emaillink{mokrovsimon@gmail.com} &
  \mobilesymbol\enspace +31 (06) 579-875-47 &
  \faLinkedin\enspace \href{https://www.linkedin.com/in/sem-wett/}{linkedin.com/in/sem-wett} \\[4pt]

  \emailsymbol\enspace \emaillink{simon.mokrov@hva.nl} &
  \faWhatsapp\enspace \href{https://wa.me/310657987547}{+31 (06) 579 875 47} &
  \faTelegram\enspace \href{https://t.me/sem_wett}{sem\_wett} \\[4pt]

  \faGithub\enspace \href{https://github.com/semwett0301}{github.com/semwett0301} &
  \faGitlab\enspace \href{https://gitlab.com/semen.mokrov}{gitlab.com/semen.mokrov} &
  \faLanguage\enspace English \,|\, Russian \,|\, Dutch (A1) \\
\end{tabular*}

\section{ABOUT ME}
\textbf{Frontend Developer} with almost \textbf{4 years} of total experience building modern, responsive, and high-performance web applications. Skilled in React, Redux (RTK), TypeScript, Next.js, Vue.js, and modern CSS frameworks, with hands-on expertise in state management, component-driven design, and frontend testing (Jest, Vitest, Cypress). \\ [0.5em]
\textbf{Professional experience} spans enterprise retail, EdTech, and banking software, with a proven track record in improving application performance, user experience, and scalable frontend architectures. \\ [0.5em]
Holds a \textbf{Master’s in Digital Driven Business} (AUAS, Amsterdam), specializing in data-driven development, machine learning, and statistics. Open to frontend-focused roles that leverage strong React and TypeScript expertise while drawing on full-stack knowledge when needed.

\section{FRONTEND EXPERIENCE (≈ 4 YEARS)}

\begin{enumerate}[leftmargin=1em, itemsep=0.01em, labelsep=0.2em, topsep=0em]

  \item \textbf{\color{darkblue} Frontend Developer} \hfill \textit{March 2024 -- Present} \\ [0.5mm]
  \small{\textit{\textbf{X5 Tech} --- Largest retail in Russia}} \\ [1mm]
  \small{Developed and supported subscription services ("Package", "Abonement") within a cross-functional environment, focusing on usability, modular architecture, and scalability.} \\ [1mm]
  {\small \textbf{Tech stack:} React, TanStack Query, pnpm, Axios, Chart.js, Python \& FastAPI (reading)}
  {\small
    \vspace{-0.5mm}
    \begin{itemize}[leftmargin=1.2em, itemsep=0.1em, topsep=0em, partopsep=0pt]
      \item Increased customer retention by 12\% through new UI features and smoother subscription flows.
      \item Reduced release time-to-market by 15\% by streamlining the frontend CI/CD pipeline.
      \item Accelerated feature delivery by 10\% using Scrum practices and modular React components.
      \item Reduced production issues by 18\% after frontend refactoring and improved error handling.
    \end{itemize}
  }

  \item \normalsize{\textbf{\color{darkblue} Full Stack Developer (Frontend-focused)} \hfill \textit{Nov 2023 -- Apr 2024}} \\ [0.5mm]
  \small{\textit{\textbf{Tune IT} --- EdTech solutions}} \\ [1mm]
  \small{Led frontend development of the Skillfactory educational platform and the Polytech admissions system, improving scalability and user experience.} \\ [1mm]
  {\small \textbf{Tech stack:} React, TypeScript, RTK Query, SCSS, Styled Components, Spring Cloud, Java, Kotlin} 
  {\small
    \vspace{-0.5mm}
    \begin{itemize}[leftmargin=1.2em, itemsep=0.1em, topsep=0pt, partopsep=0pt]
      \item Resolved 30+ UI and logic issues, increasing platform stability and reliability.
      \item Reduced design-to-development cycle by 25\% with a reusable UI component library.
      \item Adopted micro-frontend architecture, reducing average build time by 18s.
      \item Cut service latency by 13\% through modularization with Spring Cloud.
    \end{itemize}
  }

  \item \normalsize{\textbf{\color{darkblue} Full Stack Developer (Frontend-focused)} \hfill \textit{Mar 2023 -- Nov 2023}} \\ [0.5mm]
  \small{\textit{\textbf{MagicGophers} --- Social apps for VK (largest social network in Russia)}} \\ [1mm]
  \small{Developed VK mini-apps for third-party clients with a focus on interactive UI and performance.} \\ [1mm]
  {\small \textbf{Tech stack:} React, VK UI, VK Bridge, VK Router, VK API, NestJS, PostgreSQL, Redis} 
  {\small
    \vspace{-0.5mm}
    \begin{itemize}[leftmargin=1.2em, itemsep=0.1em, topsep=0pt, partopsep=0pt]
      \item Delivered apps used by 10,000+ VK users within 6 months.
      \item Increased user conversion by 20\% through UI/UX enhancements.
      \item Reduced bug reports by 30\% within 6 months.
    \end{itemize}
  }

  \item \normalsize{\textbf{\color{darkblue} Frontend Developer} \hfill \textit{July 2022 -- Mar 2023}} \\ [0.5mm]
  \small{\textit{\textbf{ITMO University} --- EdTech (remote exam monitoring)}} \\ [1mm]
  \small{Redesigned and optimized the frontend for ITMOproctor, a system for monitoring online exams.} \\ [1mm]
  {\small \textbf{Tech stack:} React, Redux, Vue.js, JavaScript, WebRTC, WebSockets, Axios} 
  {\small
    \vspace{-0.5mm}
    \begin{itemize}[leftmargin=1.2em, itemsep=0.1em, topsep=0pt, partopsep=0pt]
      \item Reduced time-to-market for new features by 20\% through modular architecture.
      \item Improved load times by 10\% via optimized state management and socket handling.
      \item Supported 5,000+ concurrent secure exam streams using WebRTC.
    \end{itemize}
  }
\end{enumerate}


\section{BACKEND EXPERIENCE}

\begin{enumerate}[leftmargin=1em, itemsep=0.01em, labelsep=0.2em]
  \item \normalsize{\textbf{\color{darkblue} Backend Developer} \hfill \textit{July 2024 -- Feb 2025}} \\ [0.5mm]
  \small{\textit{\textbf{ITMO University} --- Banking software for Gazprombank}} \\ [1mm]
  \small{Enhanced enterprise-grade backend systems for bank guarantees, focusing on efficiency and reliability.} \\ [1mm]
  {\small \textbf{Tech stack:} Java, Kotlin, Spring Boot, Gradle, PostgreSQL, Kafka, SOAP, Docker} 
  {\small
    \vspace{-0.5mm}
    \begin{itemize}[leftmargin=1.2em, itemsep=0.1em, topsep=0pt, partopsep=0pt]
      \item Reduced average response latency by 12\% through endpoint optimization.
      \item Improved PostgreSQL query execution speed by up to 20\%.
      \item Cut report build time from 90s to 60s.
      \item Lowered server load by 20\% after migrating asynchronous processing to Kafka.
    \end{itemize}
  }

  \item \normalsize{\textbf{\color{darkblue} Backend Developer (Internship)} \hfill \textit{Jan 2022 -- Jun 2022}} \\ [0.5mm]
  \small{\textit{\textbf{ITMO University} --- EdTex (OpenEdu - online learning platform)}} \\ [1mm]
  \small{Refactored a legacy Spring monolith (course update flow) and delivered a standalone certificate service.} \\ [1mm]
  {\small \textbf{Tech stack:} Java, Spring (Spring Boot), Quarkus, Hibernate, Micrometer, PostgreSQL, MinIO, Docker}
  {\small
    \vspace{-0.5mm}
    \begin{itemize}[leftmargin=1.2em, itemsep=0.1em, topsep=0pt, partopsep=0pt]
      \item Refactored the course update flow in the monolith, reducing median request latency by 8\%.
      \item Built a Quarkus-based certificate service with Hibernate, decoupling issuance from the monolith and enabling independent scaling.
    \end{itemize}
  }
\end{enumerate}


\section{RELATED EXPERIENCE}

\begin{enumerate}[leftmargin=1em, itemsep=0.01em, labelsep=0.2em]
  \item \textbf{\color{darkblue} Machine Learning Engineer, X5 Tech} \hfill \textit{Feb 2025 -- Apr 2025} \\
  {\small \textbf{Tech stack:} Python, pandas, scikit-learn, SHAP, XGBoost}\\
  {\small Built a churn prediction model and pricing simulation pipeline for subscriptions. Integrated results into dashboards and validated impact with A/B testing, supporting pricing optimization.}

  \item \textbf{\color{darkblue} Teaching Assistant, ITMO University} \hfill \textit{Sep 2022 -- Feb 2023} \\
  {\small \textbf{Tech stack:} Java, Spring Boot, PHP, JavaScript, React, Vue.js, Angular, HTML, CSS \\
  Mentored students in programming and web development. Conducted Java sessions and supported full-stack project work, strengthening technical and teaching expertise.}

  \item \textbf{\color{darkblue} CMS on FastAPI} \hfill \textit{2024} \\
   {\small \textbf{Tech stack:} Python, FastAPI, PostgreSQL, HTML, CSS, Vue.Js, Vuex \\
  Built a CMS in a team project using FastAPI and PostgreSQL. Delivered a scalable solution with authentication, relational data modeling, and a custom admin interface.}
\end{enumerate}

\section{SKILLS}
{\renewcommand{\arraystretch}{1.1}
\setlength{\tabcolsep}{4pt}
\begin{tabularx}{\linewidth}{@{}>{\bfseries}l >{}X@{}}

Frontend frameworks & React, Next.js, Vue.js (Vue + Vue Router), Electron, React Native, Expo, Angular, RxJS \\ [0.4em]

State management & Redux (RTK), TanStack Query, RTK Query, Vuex \\ [0.4em]

Frontend styling & Styled Components, Material UI, PrimeVue, Consta UI, CSS3 (Flexbox, Grid), HTML5, responsive \\ [0.4em]

Build tooling & pnpm, npm, Webpack, Vite, Babel, ESLint, Prettier, Stylelint, turborepo, webpack module federation \\ [0.4em]

Networking & WebSockets, Socket.IO, WebRTC, GraphQL, RESTful APIs, Axios, Server-Sent Events (SSE) \\ [0.4em]

Programming languages & TypeScript, JavaScript (ES6+), Java, Kotlin, Python, C \\ [0.4em]

Testing & Vitest, Jest, JUnit, Cypress, Playwright \\ [0.4em]

Backend frameworks & Spring Boot (Data, Security, MVC, JTA), Java EE, Quarkus, NestJS, FastAPI \\ [0.4em]

Databases & PostgreSQL, MySQL, Oracle, MongoDB, Redis \\ [0.4em]

DevOps & Docker, Git (GitHub, GitLab), CI/CD pipelines, AWS, Nginx, monorepo management \\ [0.4em]

Machine learning & NumPy, pandas, scikit-learn, PyTorch, XGBoost, Scrapy, Selenium \\

\end{tabularx}
}
\section{EDUCATION}
\vspace{0.5em}
% Регулируемый зазор между колонками образования
\newlength{\EduGap}
\setlength{\EduGap}{4mm} % поменяй на 6mm/10mm как нужно

% --- Две колонки EDUCATION без multicol ---
\noindent
\begin{minipage}[t]{\dimexpr0.5\linewidth-0.5\EduGap\relax}
  \educationentry[]
    {AUAS (HvA)}
    {Amsterdam, the Netherlands}
    {Master}
    {Digital Driven Business}
    {2024 -- 2025}
    {MSc}
    {
      \item Statistical testing
      \item Machine learning
      \item Clustering
      \item Deep learning
      \item Scrapy \& Selenium
      \item RecSys
      \item MLR models
      \item Research skills
    }

  \vspace{0.2em}\dotfill\vspace{0.7em}

  \educationentry[]
    {Ozyegin University}
    {Istanbul, Turkey}
    {Bachelor}
    {Computer Science (exchange)}
    {2023 -- 2023}
    {BSc -- Exchange semester}
    {
      \item Testing and analyzis
      \item Parallel Computing
      \item Advanced Databases
      \item Computer Networks
    }
\end{minipage}
\hspace{\EduGap}%
\begin{minipage}[t]{\dimexpr0.5\linewidth-0.5\EduGap\relax}
  \educationentry[]
    {ITMO University}
    {Saint-Petersburg, Russia}
    {Bachelor}
    {Software Engineering}
    {2020 -- 2024}
    {BSc}
    {
       \item Advanced and computational math
       \item Probability and queueing theory
       \item Web and low-level programming
       \item Algorithms and data structures
       \item Operating systems
       \item Databases
       \item Patterns
       \item Microservices
    }
\end{minipage}


% \section{LANGUAGES}
% \begin{tabularx}{\linewidth}{>{\bfseries}l@{\hskip 2mm --- \hskip 2mm}X}
% English & C1 (IELTS) \\
% Russian & Native \\
% Dutch & A1
% \end{tabularx}

% ... остальной правый контент ...

\end{document}
